%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{multicol}
\usepackage[none]{hyphenat}

 
\begin{document}

\header{nicola }{du toit}{user experience designer} % Your name and current job title/field
%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
18 Gordon Rd
Observatory
Cape Town
South Africa
~
083 256 7666
021 448 2040
~
\href{mailto:nicoladutoit@gmail.com}{nicoladutoit@gmail.com}
\href{http://www.nicoladutoit.com}{www.nicoladutoit.com}
\href{https://twitter.com/sophdex}{twitter.com/sophdex}
\href{http://za.linkedin.com/in/nicoladutoit/}{linkedin.com/in/nicoladutoit}
\section{languages}
english 
afrikaans
\section{personal info}
age: 31
nationality: South African
ID: 8404120820085
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011 -- 2014}
{\textbf M. Phil. in Information Technology}
{University of Cape Town}
{\textbf{Coursework:} \emph{Computer Networks, Cyberlaw and Ethics, Object-orientated Programming (Java), Web Programming, Database Systems, Human Computer Interaction, Software Engineering, Research Methods.}\\
\textbf{Dissertation:} \emph{Designing an interface to provide new
functionality for the post-processing of
web-based annotations.}}
%------------------------------------------------
\entry
{2008 -- 2010}
{\textbf 1st year Bachelor of Science}
{University of South Africa}
{\emph{Computer Science, Mathematics, Physics, Astronomy.}}
%------------------------------------------------
\entry
{2004 -- 2007}
{\textbf Bachelor of Music}
{University of Cape Town}
{\emph{with distinction in Chamber Music.}}
%------------------------------------------------
\entry
{2002 -- 2003}
{\textbf 1st and 2nd year Bachelor of Arts}
{University of the Witwatersrand}
{\emph{Music, Psychology, Law, Economics and International Relations.}}
%------------------------------------------------
\entry
{2001}
{\textbf I.E.B. Matric Certificate }
{Redhill High School}
{\emph{With distinctions for English, Afrikaans, Maths, History, French, Music.}}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{Mar 2015 -- }
{Pearson South Africa}
{Cape Town}
{\emph{User experience designer.}}
%------------------------------------------------
\entry
{Oct 2014 -- \\ Feb 2015}
{iKineo (part-time)}
{Cape Town}
{\emph{Project/product manager.}}
%------------------------------------------------
\entry
{Sept 2014 -- \\Feb 2015}
{Xendica (part-time)}
{Cape Town}
{\emph{User experience designer and front-end developer.}}
%------------------------------------------------

\entry
{2011 -- 2014}
{Siyavula Education}
{Cape Town}
{\emph{User experience designer, project manager, webmaster, quality assurance (QA) tester, copywriter, Mathematical Literacy textbook content coordinator \& author.}}
%------------------------------------------------

\entry
{2010 -- 2011}
{Barrington Studios}
{Cape Town}
{\emph{Co-founder \& co-manager of music studio and live performance venue.}}
%------------------------------------------------



\entry
{}
{Ifo Music}
{Cape Town}
{\emph{Administrator \& project manager.}}
%------------------------------------------------

\entry
{2009 -- 2011}
{Tiny Sunshine Music}
{Cape Town}
{\emph{Co-founder. Artists \& events manager. Virtual assistant \& project administrator.}}
%------------------------------------------------


%\entry
%{2008 -- 2010}
%{St Cyprian's School}
%{Cape Town}
%{\emph{Part-time cello teacher, Grades R-12.}}
%------------------------------------------------
\entry
{2008 -- 2009}
{classical.com}
{London/Cape Town}
{\emph{Web content editor \& graphic designer.}}
%------------------------------------------------


\entry
{2008 -- 2011}
{Self-employed}
{Cape Town}
{\emph{Freelance project administrator, web \& graphic designer, virtual assistant, copywriter and musician.}}
%------------------------------------------------

\end{entrylist}

\newgeometry{left=2.5cm, right=2.5cm, top=2.5cm}
\renewcommand{\entry}[4]{%
  #1&\parbox[t]{13.5cm}{%
    \textbf{#2}%
    \hfill%
    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
    #4\vspace{3\parsep}%
  }\\}
%----------------------------------------------------------------------------------------
%	PORTFOLIO SECTION
%----------------------------------------------------------------------------------------

\section{portfolio}
\begin{sitelist}

%------------------------------------------------

\site
{Mar 2015 --}
{Pearson South Africa}
{}
{\emph{Ongoing work on proprietary products which unfortunately cannot be shared yet. Work includes web, Android and iOS platforms; UX research, design and usability testing from primary school to post school level.}  }



%------------------------------------------------


\site
{2013}
{The Thunderbolt Kids: \href{http://thunderboltkids.co.za}{\underline{thunderboltkids.co.za}}}
{}
{\emph{UX, project management, project specification, research, site structure, testing.}}

%------------------------------------------------

\site
{2012 -- 2014}
{Siyavula Education: \href{https://web.archive.org/web/20140723153945/http://www.siyavula.com}{\underline{www.siyavula.com}}}
{}
{\emph{UX, project management, project specification, collaborative graphic design, copywriting, testing.}}

%------------------------------------------------

\site
{2012 -- 2014}
{Everything Maths and Science: \href{http://www.everythingmaths.co.za}{\underline{everythingmaths.co.za}} and \href{http://www.everythingmaths.co.za}{\underline{everythingscience.co.za}}}
{}
{\emph{UX, comprehensive user-centred research, project specification, graphic design, copywriting, testing.}}

%------------------------------------------------

\end{sitelist}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{skills}

\begin{itemize}
\item User experience and interface design, including responsive/mobile design.
\item Usability test design, facilitation and analysis.
\item User-centred design techniques including stakeholder interviews, focus groups, contextual inquiries, prototyping and heuristic evaluation.
\item Apple iOS and Android app design. 
\item Workshop and participatory design facilitation.
\item Project management and administration.
\item Quality assurance testing.
\item Graphic and web design, webmastering, desktop publishing, research.
\item English and Mathematics authoring, editing, proof-reading and copywriting.\\

\end{itemize}



\textbf{Operating systems}
\begin{multicols}{2}
\begin{itemize}
 \item Apple OSX, iOS
 \item Microsoft Windows
 \item Ubuntu
% \item Apple iOS
 \item Android
\end{itemize}
\end{multicols}

\textbf{Notable software}
\begin{multicols}{2}
\begin{itemize}
 \item GitHub
 \item UXPin
\item Balsamiq
% \item Axure
 \item LaTeX
 \item GVim
 \item Jekyll
   \item Adobe Creative Cloud \\ (Photoshop, InDesign, Illustrator)
\end{itemize}
\end{multicols}

\textbf{Markup and programming languages}\\

Comprehensive knowledge of: 
\begin{itemize}
 \item HTML5
 \item CSS3
 \item XML
 \item CNXML+
 \item MathML
 \end{itemize}
Sound working knowledge of Javascript, JQuery and Python.\\

\textbf{Other}
\begin{itemize}
\item Knowledge of and experience with Bootstrap, Wordpress, Plone, EPUB3.0 and Google Analytics.
 \item Fluency in English and conversational Afrikaans, working knowledge of French.\\
 
\end{itemize}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{publications}
\begin{entrylist}
%------------------------------------------------
\entry
{Jun 2014}
{Designing an interface to provide new
functionality for the post-processing of
web-based annotations}
{University of Cape Town}
{\emph{
Dissertation submitted in partial fulfilment of the requirements
for the degree of Master of Philosophy in Information Technology.} 
 }



%------------------------------------------------
\entry
{Jan 2013}
{Everything Maths Literacy Grade 10}
{Siyavula Education}
{\emph{Project management, textbook content coordination, authoring, editing, graphic design, proofreading.}}
%------------------------------------------------

\entry
{Jan 2012}
{Everything Maths Grade 10}
{Siyavula Education}
{\emph{Technical editing, textbook authoring, graphic design, proofreading.}}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORKSHOPS SECTION
%----------------------------------------------------------------------------------------

\section{workshops and conferences}

\begin{entrylist}
%------------------------------------------------
\entry
{Nov 2015}
{UX South Africa Conference}
{Cape Town}
{\emph{Conference paper/presentation entitled "UX in the real world (or how an electric can opener changed my life)"}}

\entry
{Jul 2012}
{WYSIWHAT?}
{Berlin}
{\emph{Invited to participate in a week-long sprint to develop a new WYSIWYG editor, with collaborators from Sourcefabric, Connexions, and the OERPUB collective.}}

%------------------------------------------------
\entry
{Dec 2012}
{Open Education Resources Developer Workshop}
{Google, Mountain View}
{\emph{Invited to participate in a workshop on global OER education initiatives, with Google developers, the Hewlett Foundation and developers from international organizations working on open source education issues.}}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2004 -- 2006}
{University of Cape Town Dean's Merit List}
{Cape Town}
{}
%------------------------------------------------
\entry
{2002 -- 2003}
{University of the Witwatersrand Dean's Merit List}
{Johannesburg}
{}
%------------------------------------------------
\entry
{2002}
{University of the Witwatersrand Council Entrance Scholarship}
{Johannesburg}
{}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{professional qualifications}

\begin{entrylist}
%------------------------------------------------
\entry
{2009}
{International Computer Driving License}
{ICDL via UNISA}
{\emph{Microsoft Windows, Microsoft Office, Internet}}

%------------------------------------------------
\entry
{2008}
{Licentiate of the Associated Board of the Royal Schools of Music}
{ABRSM}
{\emph{Performance, cello}}

%------------------------------------------------
\entry
{2003}
{Diploma of the Associated Board of the Royal Schools of Music}
{ABRSM}
{\emph{Performance, cello}}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER SECTION
%----------------------------------------------------------------------------------------

\section{other}
\begin{itemize}
\item Member of the ACM Special Interest Group for Computer Human Interaction (SIGCHI)
\end{itemize}

\begin{itemize}
\item Member of the Golden Key International Honour Society\\
\end{itemize}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{Professional:} human-computer interaction, cognitive psychology, accessibility, service design, visual design.

\textbf{Personal:} music, science, literature, photography, trail running, flyball (dog agility).

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

%\section{references}

%\textbf{Joanne Halse}\\
%Director, Media Hub \\
%Pearson Education \\
%joanne.halse@pearson.com\\
%\\
%\textbf{Carl Scheffler}\\
%Data Scientist\\
%Takealot\\
%carl.scheffler@gmail.com\\

%\begin{table}[h]
%\begin{tabular}{lll}
% Joanne Halse  &  \hspace{3em}  & Dr Carl Scheffler \\
%Pearson Education South Africa &    & takealot.com\\
%joanne.halse@pearson.com &    & carl.scheffler@gmail.com \\
%\end{tabular}
%\end{table}



\end{document}
